\section{\mt{Raktárak}{Storages}}

\block{
	\subsection{\mt{Raktárak lekérése}{Retrieval of storages}}

	\getbox {/warehouses/\param{warehouse}/storages?\allowbreak q=\param{q}\&archived=\param{archived}\&\allowbreak offset=\param{offset}\&\allowbreak limit=\param{limit}}
}
\params {
	\warehouseParam

	\paginatorParamA
}
\requestHeader{
    \token
}
\listCodes
\responseHeader{
    \contentJson
}
\response{
	\mt{Egy \struct{Storage} objektum lista.}{A JSON object where the key is the id of the storage and it's value is the name of the storage}
	
	\lstinputlisting{storages.list.response.json}
}

\block{
	\subsection{\mt{Raktár azonosítójának változtatása}{Changing the identifier of the storage}}

	\postbox {/warehouses/\param{warehouse}/storages}
}
\params {
	\warehouseParam
}
\requestHeader{
    \token

    \contentJson
}
\request{
	\mt{Egy \struct{MoveRequest} objektum.}{Changes the identifier of the given storage.}
	
	\lstinputlisting{storages.move.request.json}
}
\moveCodes

\block{
	\subsection{\mt{Raktár lekérése}{Retrieval of storage}}

	\getbox {/warehouses/\param{warehouse}/storages/\param{storage}}
}
\params {
	\storageParam
}
\requestHeader{
    \token
}
\getCodes
\responseHeader{
    \contentJson
}
\response{
	\mt{Egy \struct{Storage} objektum.}{The name of the storage in JSON format.}
	
	\lstinputlisting{storages.get.response.json}
}

\block{
	\subsection{\mt{Raktárak módosítása, létrehozása}{Creating, modifying storages}}

	\putbox {/warehouses/\param{warehouse}/storages/\param{storage}?\allowbreak update=\param{update}\&create=\param{create}}
}
\params {
	\storageParam

	\putParam
}
\requestHeader{
    \token

    \contentJson
}
\request{
	\mt{Egy \struct{StoragePutRequest} objektum.}{The properties of the storage in JSON format}
	
	\lstinputlisting{storages.put.request.json}
}
\putCodes

\block{
	\subsection{\mt{Raktár törlése}{Delete a storage}}

	\deletebox {/warehouses/\param{warehouse}/storages/\param{storage}}
}
\params {
	\storageParam
}
\requestHeader{
    \token
}
\deleteCodes

\block{
	\subsection{\mt{Keresés a raktárban}{Search in the storage}}

	\getbox {/warehouses/\param{warehouse}/storages/\param{storage}/search?\allowbreak q=\param{q}\&\allowbreak warehouse=\param{qwarehouse}\&\allowbreak storage=\param{qstorage}\&\allowbreak lot=\param{lot}\&\allowbreak serial=\param{serial}}
}
\params {
	\storageParam

	\searchParam
}
\requestHeader{
    \token
}
\getCodes
\responseHeader{
	\contentJson
}
\response{
	\mt{Egy \struct{ItemStack} objektum lista.}{A JSON array which contains the items as objects}

	\lstinputlisting{storages.search.response.json}
}
