\section{\mt{Telephelyek}{Warehouses}}

\block{
	\subsection{\mt{Telephelyek lekérése}{Retrieval of warehouses}}

	\getbox{/warehouses?\allowbreak q=\param{q}\&archived=\param{archived}\&offset=\param{offset}\&\allowbreak limit=\param{limit}}
}
\params {
	\paginatorParamA
}
\requestHeader{
    \token
}
\getCodes
\responseHeader{
    \contentJson
}
\response{
	\mt{Egy \struct{Warehouse} objektum lista.}{A JSON object where the key is the id of the warehouse and it's values are the properties of the warehouse}
	
	\lstinputlisting{warehouses.list.response.json}
}

\block{
	\subsection{\mt{Telephely azonosítójának változtatása}{Changing the identifier of the warehouse}}

	\postbox {/warehouses}
}
\requestHeader{
    \token
    
    \contentJson
}
\request{
	\mt{Egy \struct{MoveRequest} objektum.}{Changes the identifier of the given warehouse}

	\lstinputlisting{warehouses.move.request.json}
}
\moveCodes

\block{
	\subsection{\mt{Telephely lekérése}{Retrieval of warehouse}}

	\getbox {/units/\param{warehouse}}
}
\params {
	\apiinlineitem{warehouse}{\mt{Telephely azonosítója}{Identifier of the warehouse}}
}
\requestHeader{
    \token
}
\getCodes
\responseHeader{
    \contentJson
}
\response{
	\mt{Egy \struct{Warehouse} objektum.}{The properties of the warehouse in JSON format.}
	
	\lstinputlisting{warehouses.get.response.json}
}

\block{
	\subsection{\mt{Telephely módosítása, létrehozása}{Creating, modifying warehouses}}

	\putbox {/warehouses/\param{warehouse}?update=\param{update}\&create=\param{create}}
}
\params {
	\warehouseParam

	\putParam
}
\requestHeader{
    \token
    
    \contentJson
}
\request{
	\mt{Egy \struct{WarehousePutRequest} objektum.}{The properties of the warehouse in JSON format.}
	
	\lstinputlisting{warehouses.put.request.json}
}
\putCodes

\block{
	\subsection{\mt{Telephely törlése}{Delete a warehouse}}

	\deletebox {/warehouses/\param{warehouse}}
}
\params {
	\warehouseParam
}
\requestHeader{
    \token
}
\deleteCodes

\block{
	\subsection{\mt{Keresés a telephelyen}{Search in the warehouse}}

	\getbox {/warehouses/\param{warehouse}/search?\allowbreak q=\param{q}\&warehouse=\param{qwarehouse}\&storage=\param{qstorage}\&\allowbreak lot=\param{lot}\&serial=\param{serial}}
}
\params {
	\warehouseParam

	\searchParam
}
\requestHeader{
    \token
}
\getCodes
\responseHeader{
	\contentJson
}
\response{
	\mt{Egy \struct{ItemStack} objektum lista.}{A JSON array which contains the items as objects}

	\lstinputlisting{warehouses.search.response.json}
}
